\input{preamble.tex}

\usepackage{ragged2e}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{ }
\usepackage[a4paper, top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}

\begin{document}
  
\recipient{[PLACEHOLDER COMPANY]}{[PLACEHOLDER LOCATION]}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,\vspace{-2em}}
\makelettertitle
\justifying

I am writing to express my interest in pursuing a [PLACEHOLDER POSITION] position at [PLACEHOLDER COMPANY]. With a strong academic background in Mathematical and Computer Sciences, a passion for distributed systems and networking, and a track record of successful projects, I believe I am well-suited for the challenges and opportunities in your organization.

As highlighted in my attached resume, I am currently pursuing a Bachelor's degree in Mathematical and Computer Sciences at The University of Adelaide, where I have consistently maintained a GPA of 6.5/7.0. This program has equipped me with a solid foundation in computer science principles, including distributed systems and networking. I am eager to apply my knowledge and skills to real-world projects in a professional setting.

During my previous role as a Network/System Engineer at Global Technology Integrator Ltd., I spearheaded automation and parallelization efforts to optimize tasks such as account migration and registry modification. By reducing manpower and time required for each task, I successfully addressed staff shortages while maintaining high-quality outcomes. Additionally, I took on the responsibility of mentoring new staff members, helping them understand the technologies we utilized. My experience in this role has honed my problem-solving abilities and enhanced my teamwork and communication skills.

I am particularly proud of the projects I have completed, which demonstrate my technical capabilities and creativity. For instance, my project "Binary Search on Color" utilized the binary search algorithm to find the color closest to the user's desired color, aiding in decision-making processes. Another project, "The Sound of Personality," involved leveraging the Spotify API to estimate users' MBTI types based on their music preferences. These projects showcased my ability to quickly adapt to new technologies and work effectively within a team.

In addition to my technical expertise, I have actively engaged in volunteer work to further develop my leadership and organizational skills. As a Software Developer for the Adelaide Rover Team, I have efficiently organized and structured projects, ensuring optimal outcomes. I have also contributed to the success of UNIHACK by handling logistics and marketing, and I have updated The University of Adelaide Computer Science Club's website to provide up-to-date information about events.

My skills encompass a range of programming languages, including C++, JavaScript, Python, and more. I am a fluent English speaker and possess native proficiency in Cantonese, advanced proficiency in Mandarin, and beginner-level proficiency in German. Furthermore, I have received recognition for my academic performance, receiving the subject prize in Information and Communication Technology in 2021 and being awarded the University of Adelaide's 30\% Global Citizens Scholarship.

I am excited about the opportunity to contribute my skills, knowledge, and enthusiasm to [PLACEHOLDER COMPANY]. I am confident that my dedication to excellence, strong problem-solving abilities, and passion for technology make me a valuable asset to any software engineering team. I am open to exploring various roles within your organization, and I am eager to contribute to its success.

Thank you for considering my application. I look forward to the possibility of discussing how my qualifications align with your company's goals. Please find my attached resume for your reference. Should you require any additional information, please do not hesitate to contact me.

\vspace{1em}
\makeletterclosing

\end{document}
