\input{preamble.tex}

\usepackage[scale={0.925, 0.925}]{geometry}

\begin{document}
  \makecvtitle{}

  \vspace{-2.3em}
  \section{Education}
    \cventry{2022 Jan -- 2024 Dec}{Bachelor of Computer Science}{The University of Adelaide}{Australia}{\textit{GPA: 6.5/7.0}}{}

  \section{Experience}
    \cventry{2021 Aug -- 2021 Nov}{System Engineer}{Global Technology Integrator Ltd.}{Hong Kong}{}{I spearheaded the automation of our tasks using BAT scripts, including the migration of local accounts to AD accounts and modification of the registry, which enabled parallelization and reduced the human resources needed. Although the original scope of my job was only to do these tasks manually, my efforts to automate them were still greatly appreciated by my supervisors and colleagues as we would not have been able to finish the project on time due to the staff shortage. }
    
  \section{Projects}
    \cventry[0.5em]{2022 Nov -- Present}{HTML, CSS, JavaScript}{Negative Base Converter}{Australia}{}{This is a web app that converts numbers from any base to any other base, including negative bases, which have the unique property of being able to represent all positive and negative integers without using a negative sign. As this topic is not very popular, I had to do a lot of research in order to discover an algorithm that can deal with the conversion properly especially when it comes to fractional numbers. }
    \cventry[0.5em]{2022 Sep -- 2022 Oct}{C++, Make, \LaTeX}{Pokemon Battles}{Australia}{}{My team and I created a text-based, turn-based, player vs. computer Pokemon battle game. The player can choose from a selection of Pokemon and battle against a computer-controlled opponent. I led the coding part of the project, and since my teammates were not as familiar with C++, I often tried to help them learn some of the more difficult concepts and helped them succeed in this course even outside of this project. }
    \cventry[0.5em]{2022 Apr -- 2022 May}{MATLAB}{MATLAB Minigames}{Australia}{}{I created multiple games within MATLAB including minesweeper and blackjack. This was a fun project that introduced me to algorithm design as I implemented my first flood fill algorithm. }
    \cventry{2021 Sep -- 2021 Dec}{Python, Pillow}{allRGB}{Hong Kong}{}{This is part of a bigger project started by "deidee", which has the objective to create images with one pixel for every RGB color, without any duplicate or missing colors. I aimed to create a Python program that would take any image and convert it into an allRGB image. As this was my first programming project ever, my program used the brute-force solution, and although functional, it was quite inefficient. Now that I am more familiar with algorithm design and data structures, I plan to rewrite the program to make it more efficient. }
    
  \section{Community involvement}
      \cventry{2022 Dec -- Present}{Committee Member}{The Computer Science Club at The University of Adelaide}{Australia}{}{As a committee member, I initiated the process of updating the club's website in order to provide up-to-date information regarding our events for our members, which taught me some web development skills. }

  \section{Skills \& Achievements}
    \subsection{Languages}
      \cvdoubleitem{Proficient}{C++}{\hspace*{-\textwidth}\hfill{}Intermediate / Beginner}{Bash, C, CSS, HTML, JS, \LaTeX{}, MATLAB, Python}

    \subsection{Prizes}
      \cvitemwithcomment{Subject prize}{ICT 2021}{Achiever of the best results amongst peers}

    \subsection{Scholarships}
      \cvitemwithcomment{University of Adelaide}{30\% Global Citizens Scholarship}{Best possible scholarship for international students}

\end{document}
